Report

### 2021-04-29 Rmd/report.Rmd
Generate new report

# load packages
library(papaja)
library(knitr)
library(tidyverse)
library(readxl)
library(lubridate)
library(scales)
library(patchwork)
library(here)

# load functions
source(here("R", "utils.R"))

# load data
stimuli <- readRDS(here("Results", "stimuli.rds"))
participants <- readRDS(here("Results", "participants.rds"))
gaze_trial <- readRDS(here("Results", "gaze_trial.rds"))
gaze_time <- readRDS(here("Results", "gaze_time.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
fit <- readRDS(here("Results", "fit_trials.rds"))
```

@@

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# plot participants
participants %>% 
	drop_na() %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(~age_group) +
	geom_bar() +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "N", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(axis.title.x = element_blank()) +
	ggsave(here("Figures", "sample.png"))
```

@@

@@

col <- ifelse(distinct(attrition, participant, valid_participant)$valid_participant, "#377EB8", "#E41A1C")

attrition %>% 
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Invalid"),
		   participant = paste0(participant, " (", missing_n, ", ", percent(missing_prop), ")")) %>% 
	ggplot(aes(missing, participant, colour = valid_trial)) +
	geom_point(alpha = 0.5) +
	geom_vline(xintercept = 0.25, linetype = "dashed") +
	labs(x = "Proportion of missing trials (out of 32)", y = "Participant") +
	scale_color_brewer(palette = "Set1") +
	theme_custom() +
	theme(axis.text.y = element_text(colour = col, size = 8),
		  axis.title.y = element_blank(),
		  axis.text.x = element_text(colour = "black"),
		  legend.title = element_blank(),
		  legend.position = "top",
		  text = element_text(size = 15)) +
	ggsave(here("Figures", "missing.png"), height = 9)

@@

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# vocabulary
participants %>% 
	mutate(age_group = as.factor(age_group)) %>% 
	drop_na(lp) %>% 
	ggplot(aes(as.factor(age_group), vocab_size, colour = lp, fill = lp)) +
	geom_point(shape = 1, size = 3, stroke = 1, position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", outlier.colour = NA, position = position_dodge(width = 0.75)) +
	labs(x = "Age group (months)", y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", position = position_nudge(x = 0.2), outlier.colour = NA) +
	geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_custom() +
	theme(legend.position = "none",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial.png"))

@@

```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_point(size = 2, shape = 1, stroke = 1) +
	geom_smooth(se = FALSE, method = "lm") +
	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_custom() +
	theme(legend.position = "none",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
```

@@

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(shape = 1, stroke = 1, size = 1) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time.png"))

@@

```{r gaze_time_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, time_bin, trial_type, lp, age_group) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_wrap(age_group~participant~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(shape = 1, stroke = 1, size = 0.5) +
	geom_text(aes(x = 0, y = 1, label =
				  	paste0(str_remove_all(participant, pattern = "[a-zA-Z]"),
				  		   "/", age_group, "mo/", lp)),
			  size = 2, colour = "black", hjust = 0) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(
		axis.text = element_text(size = 7),
		legend.title = element_blank(),
		legend.position = "top",
		strip.background = element_blank(),
		strip.text.x = element_blank()
	) +
	ggsave(here("Figures", "gaze_time_participant.png"), height = 12, width = 12)
```

@@

>>>>

# load packages
library(papaja)
library(knitr)
library(tidyverse)
library(bilingualr)
library(lubridate)
library(scales)
library(janitor)
library(gt)
library(patchwork)
library(here)

# load data
participants <- readRDS(here("Results", "participants.rds"))
gaze_trial <- readRDS(here("Results", "gaze_trial.rds"))
gaze_time <- readRDS(here("Results", "gaze_time.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))

@@

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar() +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "N", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))
```

@@

This table shows a summary of the total, total valid, and proportion of valid monolingual and bilingual participants tested in each lab (Barcelona and Oxford), in each age group (21, 25, and 30 months), and the mean of valid trials they contributed in each trial type (cognate, non-cognate, and unrelated).

@@

attrition %>%
	left_join(select(participants, location, lp, participant, date_test)) %>% 
	drop_na(trial_type) %>% 
	group_by(participant, lp, location, date_test, age_group, trial_type, valid_participant, valid_other) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

@@

### vocabualry in the dominant language (L1)

This figure represents the vocabulary size in the dominant language of participants in the Y-axis and their linguistic profile in the X-axis. Results are presented separately for each age group. The shape of the violins, represents the distribution of the vocabulary sizes. The box-plot inside each violin represents the median, 25th and 75th percentiles, and the vertical lines represent the minimum and maximum values. vocabulary sizes in the dominant language were calculated as the proportion of items each participant was reported to *understand* or *understand and say* in the language of most exposure. for example, for a participant exposed mostly to Catalan, their vocabulary size in the dominant language was calculated as the proportion of words they were reported to understand and/or say in Catalan, from a total of ~200 words.

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# vocabulary
participants %>% 
	mutate(age_group = as.factor(paste0(age_group, " mo"))) %>% 
	drop_na(lp) %>% 
	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
	facet_wrap(~age_group) +
	geom_violin(position = position_dodge(width = 0.75)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

For each participant and trial, the proportion of fixations to the target object were calculated from the total of fixations to the target, the distractor, and the rest of the screen. Then proportions for the same participant were aggregated within conditions, so that for each participant three data points were obtained: one in each trial type (cognate, non-cognate, and unrelated). Some participants were longitudinal. Scores form longitudinal participant  are indicated by gray lines linking data points from the same participant.

```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "none",
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial.png"))

@@

## By age group

```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(age_group, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = interaction(participant, trial_type)), alpha = 0.5) +
	geom_violin(position = position_dodge(width = 0.5)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.5), colour = "black", fill = "white") +
	labs(x = "Age (months)", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

## Effect of vocabulary

```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	drop_na() %>% 
	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_point(alpha = 0.5) +
	geom_smooth(se = FALSE, method = "lm") +
	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		  legend.position = "top",
		  axis.text.x = element_text(size = 10)) +
	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
```

@@

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time.png"))

@@

```{r gaze_time_vocab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, vocab_size)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		vocab_cat = ifelse(
			vocab_size < median(.$vocab_size, na.rm = TRUE),
			"Below the median",
			"Above the median"
		)
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_wrap(age_group~lp~vocab_cat) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time_vocab.png"))

@@

## Appendix 1: Individual attrition rates

```{r attrition_individual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}

attrition %>%
	left_join(select(participants, location, lp, participant, date_test)) %>% 
	drop_na(trial_type) %>% 
	group_by(participant, lp, location, date_test, age_group, trial_type, valid_participant, valid_other) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(names_from = trial_type, values_from = valid_trial_count) %>% 
	clean_names() %>% 
	mutate(
		participant = str_remove(participant, "cognatepriming"),
		cognate = paste0(cognate, " (", round(cognate/8, 2), "%)"),
		non_cognate = paste0(non_cognate, " (", round(non_cognate/8, 2), "%)"),
		unrelated = paste0(unrelated, " (", round(unrelated/8, 2), "%)"),
	) %>% 
	arrange(location, date_test) %>% 
	relocate(
		participant, location, date_test,
		age_group, lp, cognate, non_cognate,
		unrelated, valid_other, valid_participant) %>% 
	gt() %>% 
	gt::tab_spanner(
		"Valid trials (%) by trial type",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		date_test = "Date",
		lp = "Group",
		age_group = "Age",
		valid_participant = "Valid trials",
		valid_other = "Valid (other)?",
		cognate = "Cognate",
		non_cognate = "Non-cognate",
		unrelated = "Unrelated"
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#00FA9A")
		),
		locations = cells_body(
			columns = c("valid_participant"),
			rows = valid_participant
		)
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#00FA9A")
		),
		locations = cells_body(
			columns = c("valid_other"),
			rows = valid_other
		)
	)

## Appendix 2: Individual target looking times

```{r gaze_time_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, time_bin, trial_type, lp, age_group) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_wrap(age_group~participant~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	# geom_point(shape = 1, stroke = 1, size = 0.5) +
	geom_text(aes(x = 0, y = 1, label =
				  	paste0(str_remove_all(participant, pattern = "[a-zA-Z]"),
				  		   "/", age_group, "mo/", lp)),
			  size = 2, colour = "black", hjust = 0) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		axis.text = element_text(size = 7),
		legend.title = element_blank(),
		legend.position = "top",
		strip.background = element_blank(),
		strip.text.x = element_blank()
	) +
	ggsave(here("Figures", "gaze_time_participant.png"), height = 12, width = 12)
```
